Automated verification of stand-alone solar photovoltaic systems

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed Threats to Validity
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Related to the four 700 W PV systems, the sizing check was successful during automated verification, but there were found flaws in everyone, all related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaws right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4. This functional problem was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\subsection{Threats to Validity}
%---------------------------------------------------
\textit{Model precision:} each component received a mathematical model, and the precision of the proposed tool depends on the precision of that model. Probably a evaluation in a laboratory to validate the model could give more reliability to the proposed tool.

\textit{Time step:} The computing complexity is a issue, but the time step of one hours can be evaluated to approximate the algorithm of the real world, where a solar irradiance and ambient temperature can change in minutes.

\textit{Case studies:} The studies were performed only at the municipality of Manaus, at the south hemisphere. A more complete evaluation can be performed if other places around the world could become case studies.

>>>>

Related to the four 700 W PV systems, the sizing check was successful during automated verification, but there were found flaws in everyone, all related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaws right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4. This functional problem was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\subsection{Threats to Validity}
%---------------------------------------------------

We have reported a favorable assessment of the proposed verification method over a diverse set of real-world benchmarks. Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.

\textit{Model precision:} each component of the PV system is mathematically modelled, and the precision of the proposed method depends on the precision of that particular model. A careful evaluation in a PV laboratory to validate the model could add more reliability to the results produced by our method.

\textit{Time step:} The runtime complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.

\textit{Case studies:} Our case studies are performed only in Manaus, in particular in the south hemisphere. A more complete evaluation can be performed if other places around the world could become case studies.
